Fourmile

### 2022-09-20 fourmile_dataprocess.Rmd
added doy to missRanger data gaps

srad_gapfil_all <- full_join(srad_gapfil, bet_day, by='date') %>%
  filter(date < '2020-12-31') %>%
  dplyr::select(-c(bet_sw_in_mjm2.x)) %>%
  rename(bet_sw = bet_sw_in_mjm2.y)

@@

new_srad <- missRanger(srad_gapfil_all, num.trees=100)
summary(new_srad)

srad_flip_fill <- new_srad %>%
  pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')

>>>>

srad_gapfil_all <- full_join(srad_gapfil, bet_day, by='date') %>%
  filter(date < '2020-12-31') %>%
  dplyr::select(-c(bet_sw_in_mjm2.x)) %>%
  rename(bet_sw = bet_sw_in_mjm2.y) %>%
  mutate(doyh = yday(date))

@@

new_srad <- missRanger(srad_gapfil_all, num.trees=100000)
summary(new_srad)

srad_flip_fill <- new_srad %>%
  dplyr::select(-c(doyh)) %>% 
  pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')
